%\textbf{Instructions: Contribution to structuring
%doctoral/early-stage research training at the European level and to
%strengthening European innovation capacity, including the potential
%for Meaningful contribution of the non-academic sector to the
%doctoral / research training (as appropriate to the implementation
%mode and research field)}  

\subsubsection{Contribution to structuring doctoral training at the European level}

%%Structuring

The academic and industrial training offered by \acronym greatly benefits ESRs by widening their career choices beyond the academic model of student-postdoc-professor.
%normally portrayed in academia. 
%As discussed in Sec.~\ref{sub:trainingOverview}, 
%\acronym structures its training following the Salzburg Principles, 
%\acronym provides a supportive environment for the development of each ESR.
Both \acronym recruitment and \textbf{training} proceeds in a diverse, inclusive, and supportive environment with the help of mentors and specific officers, complementing
taught courses at the beneficiary institutes with academic research and non-academic industrial secondments. 
Such a diverse training program mandates an attentive SC and the use of a credit system linked to the ECTS system, to quantify and evaluate ESR training progress (Sec.~\ref{sub:trainingOverview}). 
Both serve as example for the structuring of early-stage research training within \acronym. 
% of the ESR training as ,
%agreed upon by student and supervisor in the PCDP
%and then approved by the Supervisory Board. 
%Although the \acronym credit system is voluntary, 
%and its adoption is left to the PhD-awarding organizations, 
%Its direct link to the ECTS credit system serves as example 

\acronym training happens within and outside the consortium, blending with existing training programs hosted by beneficiaries and partners, as well as with ongoing ITN networks (e.g. organizing joint training with INSIGHTS).
As well as providing complementary training for ESRs, these collaborations in training offer an excellent platform to share best practices and seek complementary funding sources beyond this ITN, increasing the internationalization of the participating organizations. 
Discussions have already started among the network participants on how to share training and find funding beyond this ITN to attract and retain more talented students from abroad. The participation of the network to ISOTDAQ and MLHEP, the most important school of HEP data acquisition and ML, goes in this direction, by disseminating network results and techniques and at the same time allowing ESRs to learn the state of the art. 

%%Meaningful contribution of non-academic sector to the training
\acronym links training in HEP with commercial applications within the common ground of RTA, so that the non-academic sector strongly contributes to the increased societal
and economic relevance of the outcome of the ESR research and training path. 
The majority of ESRs will spend a minimum of three months seconded to an industrial beneficiary or partner, and will explicitly use their academic training to further the development of industrial products; in turn, the industrial training they receive will boost their academic research. 
Within \acronym, the non-academic sector is placed at the heart of the training program in a concrete and practical way, so that ESRs employ techniques developed for research
in industry and vice versa. 
This is not yet the norm in  physics graduate courses, even though studies show a need for this kind of interdisciplinary and intersectoral mobility
experience\footnote{Roach M, Sauermann H (2017) The declining interest in an academic career. PLOS ONE 12(9): e0184130, \url{http://journals.plos.org/plosone/article?id=10.1371/journal.pone.0184130}}. 
Moreover, history shows that such interdisciplinary cross-pollination of methods and problem-solving skills strengthens innovation (e.g. Bell Labs in the USA). 
We hope the success of \acronym, if funded, and of H2020 ITN programs across Europe will encourage embedding non-academic training in PhD degrees. 
\vspace{-2mm}

\subsubsection{Contribution to strenghtening the European innovation capacity}

The research and industry goals in \acronym be met using innovative techniques that are the focal point of a European-wide ESR education, benefitting both the European higher education system and Europe's innovation and growth potential. 

The economic importance of physics in European industries overall has been detailed by the CEBR\footnote{\href{http://www.eps.org/resource/resmgr/policy/EPS_economyReport2013.pdf}{The importance of physics to the economies of Europe}, Centre for Economics and Business Research Ltd, London, 2013} in a report commissioned by the European Physical Society.  
Industries for which the use of physics in terms of technologies and expertise is critical to their existence generated a turnover of \euro3.8 trillion in 2010, 15\% of the total turnover Europe's economy.  
Moreover, the productivity per employee in the physics-based industries largely outperforms that of other industries. 

%Data Science is one of the fastest
%growing sectors in the world. 
As noted by a recent report by the EU's High Level Expert Group on the European Open Science Cloud\footnote{"500,000 data scientists needed in European open research data",
A. Offermann, \url{https://joinup.ec.europa.eu/news/500000-data-scientists-need}}, expertise in Data Science is a skill needed to strenghten innovation in Europe, 
and one that \acronym ESRs will gain. 
\acronym will prepare a well-trained addition to the European workforce that will give a competitive edge to the academic institutes and industries where the ESRs will undertake their training, as well as those where they will be employed after their PhD.  
This will be increased by the strength of the network as a whole, acting coherently to improve the deployment of RTA techniques. 
In the data-rich environment that will dominate both HEP and industry, making decisions fast and efficiently becomes a priority to make an impact and
be at the forefront of innovation and developments.  

The LHC is at the forefront of big data in the scientific domain: Computing sites that are part of the Worldwide LHC Computing Grid need around 1 exabyte to store data from the LHC experiments after the trigger selection\footnote{The HEP Software Foundation, \href{https://arxiv.org/pdf/1712.06982.pdf}{A Roadmap for HEP Software and Computing R\&D for the 2020s}, ArXiv Document Server}. 
While LHC data may not be as big as for large companies, cost-effectiveness is crucial for research due to the more limited budget allocated. 
The codebase of the LHC experiments, more than 50 million lines long\footnote{Information Is Beautiful, \href{http://www.informationisbeautiful.net/visualizations/million-lines-of-code/}{Codebase infographics}, accessed online 01/2019} is larger than all but the biggest commercial projects.  
For these reasons, the LHC research ecosystem provides an ideal opportunity to develop new methods of analyzing big data in real-time, and to train ESRs in topics matching the emerging trend of \textbf{real-time big data analytics}\footnote{\href{https://www.scnsoft.com/blog/real-time-big-data-analytics-comprehensive-guide}{A comprehensive guide to real-time big data analytics.}} 

%The impact of physics is underestimated in this study, as the
%contributions of physics-trained people to the booming field of DS
%are not considered. The skill set of physicists are particularly
%appreciated in this sector, and it represents one of the main
%employers for physicists who leave academia. This can only increase
%the figures from the Cebr, establishing the impact of fundamental
%research in physics as  impactful on the European economy.


 
