%In addition to publications and patents, communication of the Marie Sk?lodowska-Curie actions should aim to demonstrate the ways in which research is contributing to a European "Innovation Union."9 It should also account for public spending by providing tangible evidence that the funded research adds value by:
%??? showing how European collaboration in the ITN has achieved more than would have otherwise been possible, notably in achieving scientific excellence, contributing to competitiveness and, where relevant, solving societal challenges;
%??? showing how the outcomes are relevant to our everyday lives, by creating jobs, training skilled researchers, introducing novel technologies, or making our lives more comfortable in other ways;
%??? promoting results, which may possibly influence policy-making or ensure follow-up by industry and the scientific community.

%YR advice:
%In 2015 and previous calls, this section was referring to effectiveness to proposed measures. As of 2016 the quality of the proposed measure seems to get more attention, we advise to be specific about the targeted journals and conferences (in case of dissemination) and about the quality of the local Tech Transfer offices of the participating universities.

%All researchers should ensure, in compliance with their contractual arrangements, that the results of their research are disseminated and exploited, e.g. communicated, transferred into other research settings or, if appropriate, commercialised. Senior researchers, in particular, are expected to take a lead in ensuring that research is fruitful and that results are either exploited commercially or made accessible to the public (or both) whenever the opportunity arises.

%which are the target audiences for dissemination:
In order for \acronym results to make an effective impact within and beyond the consortium, and to ensure a high visibility for ESRs, we identify three distinct audiences for the dissemination strategy. 
%Sentence before, removed. 
%This will ensure a high visibility to ESRs as well as contributing to the dissemination
%of the novel techniques developed to an  audience much larger
%than \acronym's.
The first is composed of the \textbf{scientists members of the LHC collaborations} that the ESRs are connected to. 
In this context, intermediate work can be shown by the ESRs, normally after discussion and preview by the supervisor. 
In addition, the ESRs will present their work regularly within \acronym at the occasion of the yearly meetings, as all four LHC collaborations allow the presentations of intermediate results within the context of regional or training network meetings after a brief review process. 

When the results are mature, they will be made public to \textbf{the wider HEP and Data Science communities}. 
This step will happen after internal peer-review from the collaborations for physics results, and after the necessary exploitation measures have been taken in case of algorithms with a commercial value. 
\acronym results will be published in high-impact Open Access journals of the most closely corresponding research field, 
whether physics or Data Science. 
The physics publications produced within the ALICE, ATLAS, CMS and LHCb collaborations fall under the CERN regulations on intellectual
property. CERN publishes following the Open Access conditions, as defined by the SCOAP3\footnote{SCOAP3, \href{http://scoap3.org/}{SCOAP3 Sponsoring Consortium for Open Access Publishing in Particle Physics.}} initiative, adopting the Creative Commons Attribution. 
%Papers with experimental results based on LHC data will mention "Copyright CERN, for the benefit of the  Collaboration".
The CERN publication policy aims to exercise the copyrights to permit the widest possible dissemination and use of the obtained results, and all \acronym publications will follow the same publication philosophy.
Examples in which \acronym members have regularly published are \href{http://journals.aps.org/prl/}{PRL}\footnote{We are aware that PRL is not Open Access or SCOAP3  compliant, but CERN articles are treated as a special case by PRL and \textbf{are} Open Access, and all \acronym publications sent to PRL will be in this category.},  
\href{http://www.journals.elsevier.com/physics-letters-b/}{PLB}, 
\href{http://jhep.sissa.it}{JHEP}, 
\href{http://jmlr.csail.mit.edu}{JMLR}, 
\href{http://www.springer.com/computer/ai/journal/10994}{ML}, 
\href{http://www.computer.org/web/tpami}{IEEE PAMI}.
All publications will also be made available on the CDS and arXiv preprint servers. 
Each ESR will be responsible for the publication of 1-2 journal papers and 1-2 conference reports during their PhD. 
\acronym members have extensive experience preparing publications in the most qualified peer-reviewed journals of their respective fields and will consequently supervise and train
ESRs to disseminate their results.  
One of the priorities of \acronym is to train ESRs in reproducible and sustainable research. 
Software toolkits will be published on \href{www.zenodo.org}{Zenodo}, so that they can be cited. 
Wherever appropriate, Jupyter notebooks and Docker images to run data analysis will be published together with research papers. 
\acronym results will also be presented in international conferences, e.g.
\href{https://indico.cern.ch/event/577856/}{EPS},
\href{http://www.ichep2018.org}{ICHEP},
\href{http://moriond.in2p3.fr}{Moriond  EW\&QCD},
\href{http://nips.cc}{NIPS}, \href{http://icml.cc}{ICML}, \href{http://www.aaai.org/Conferences/IAAI/iaai15.php}{AAAI}, \href{http://www.ecmlpkdd2014.org}{ECML},
\href{https://sites.google.com/site/representationlearning2014/}{ICLR}, \href{http://www.aistats.org}{AISTATS}, \href{http://chep2018.org}{CHEP}, \href{http://cdsr.net/papers/}{CDSR}, 
\href{https://indico.cern.ch/event/543031/}{IEEE Real Time Conference}, etc. 

Finally, reports and whitepapers delivered within the research WPs, will summarize the overall WP results with respect to the initial Network objectives, and the recommendations
made towards adopting RTA and the computing resources needed to do so. 
The target audiences here are the \textbf{EU Commission, the European researchers subscribed to the EURAXESS community}, who may find interesting links and connections between
their research and the research undertaken in \acronym and want to collaborate, as well as policymakers and research councils who can be pointed to whitepapers and recommendations, in the same fashion as for the HEP Software Foundation Whitepaper\footnote{http://hepsoftwarefoundation.org/activities/cwp.html} that encouraged DOE to fund the IRIS-HEP institute for computing in HEP in the US.  
Members of \acronym (Sokoloff, Gligorov, Boveia, Albrecht and Doglioni) are active members of the HSF and hold positions of responsibility.  
%Prof. M. Sokoloff from \cincinnatientity is one of the leaders of this important effort that joins HEP and Data Science, and V. Gligorov, A. Boveia,
%F. Winklmeier, J. Albrecht and C. Doglioni contributed to the sub-chapter on Software Trigger and Event Reconstruction. 
Boveia and Doglioni also have experience being the main organizers and editors of the Dark Matter Forum and Dark Matter Working Group whitepapers, with recommendations on Dark Matter benchmark models for the entire LHC theory and experimental community. 
Together, \acronym is equipped with  key people to achieve this dissemination goal. 

The responsible for the dedicated Dissemination and Outreach Work Package (Petersen, \cernentity) will assist the network members (ESRs and supervisors) on publication matters. 
He will also ensure that all results of \acronym and their online links are highlighted on the \acronym web page, social media and local institute press releases. 
