\begin{center}\scriptsize
begin{tabular}{|p{0.05\textwidth}|p{0.07\textwidth}|p{0.1\textwidth}|p{0.06\textwidth}|p{0.05\textwidth}|p{0.45\textwidth}|}
\hline
\pbox{8cm}{\textbf{ESR}} & 
\pbox{8cm}{\Tstrut \textbf{Recruiting} \\ \textbf{node} \Bstrut} &  
\pbox{8cm}{\Tstrut \textbf{PhD-awarding} \\ \textbf{node} \Bstrut} &  
\pbox{8cm}{\Tstrut \textbf{Planned} \\ \textbf{start} \Bstrut} &  
\pbox{8cm}{\Tstrut \textbf{Duration}} & 
\pbox{8cm}{\Tstrut \textbf{Title}} 
\tabularnewline 
\hline
%%%
\textbf{\ESRa} & \helsinkientity & \helsinkientity & 8 & 36 & ML and RTA for Higgs boson measurements and industry \tabularnewline \hline %Eerola [19], 
\textbf{SC} & \multicolumn{5}{p{0.9\textwidth}|}{
\textbf{Main supervisor: Voutilainen} (\helsinkientity), [12]. Assistant professor in particle physics. Expertise: RTA, SM and Higgs measurements, with positions of responsibility in CMS. Grant from the Finnish Academy of Science, prizes for research during PhD and postdoc. } \tabularnewline
 & \multicolumn{5}{p{0.9\textwidth}|}{\textbf{Second supervisor: Pierini} (\cernentity) [19]. CERN staff scientist. Expertise: RTA, ML for HEP. ERC Consolidator Grant for ML at the LHC.}\tabularnewline 
 & \multicolumn{5}{p{0.9\textwidth}|}{\textbf{Industrial supervisor: Taccari} (\fleetmaticsentity). Data scientist. Expertise: mathematical optimization and ML. }\tabularnewline 
 & \multicolumn{5}{p{0.9\textwidth}|}{\textbf{Senior mentor: Eerola} (\cernentity) [19]. Professor in particle physics, Vice Rector of the University of Helsinki. Expertise: B-physics (chosen Higgs decay mode for ESR thesis).}\tabularnewline 
 & \multicolumn{5}{p{0.9\textwidth}|}{\textbf{Supervising postdoc: Kirschenmann} (\helsinkientity). Expertise: LHC jet physics and searches, with positions of responsibility in CMS. } \tabularnewline \hline \hline
%%%
\textbf{\ESRb} & \unigeentity & \unigeentity & 8 & 36 & Title \tabularnewline \hline %Eerola [19], 
\textbf{SC} & \multicolumn{5}{p{0.9\textwidth}|}{
\textbf{Main supervisor: A} (\unigeentity), [N]. [Position]. Expertise: [Text]. [Qualifications and grants] } \tabularnewline
 & \multicolumn{5}{p{0.9\textwidth}|}{\textbf{Second supervisor: B} (\unigeentity) [19]. [N]. [Position]. Expertise: [Text]. [Qualifications and grants] }\tabularnewline 
 & \multicolumn{5}{p{0.9\textwidth}|}{\textbf{Industrial supervisor: C} (\fleetmaticsentity). [N]. [Position]. Expertise: [Text]. }\tabularnewline 
 & \multicolumn{5}{p{0.9\textwidth}|}{\textbf{Senior mentor: D (only needed if the main supervisor is not senior)} (\cernentity) [N]. [Position]. Expertise: [Text]. [Qualifications and grants] }\tabularnewline 
 & \multicolumn{5}{p{0.9\textwidth}|}{\textbf{Supervising postdoc: E (if available)} (\helsinkientity). Expertise: [Text]} \tabularnewline \hline \hline
 %%%
 
 \multicolumn{6}{p{0.95\textwidth}}{
\footnotesize 
\vskip2pt
Table 1.2: Recruitment deliverables per beneficiary, Supervisory Committee (SC) with number of supervised students (from the Master's degree level) and expertise/qualification of supervisors. 
\vskip2pt
\normalsize
}
\end{tabular}
\end{center}