



% AB: ever-proliferating collection, internet of things, on scales from detection of subatomic particle collisions to smart home devices to 'smart' cities (traffic flow, gunshot detection, snowplow scheduling) to the planet (shipping and inventory distribution).
% AB: the information does not generate the need. the information is collected in order to make smarter decisions. but how to quickly and efficiently make sense of this information to reach decisions?
Due to the ever increasing availability of vast amounts of information in research and industry, new \textbf{fast and efficient automated decision making techniques} are needed.
% AB: needed for what?
\textit{Fast} means that the decision needs to be taken in real-time, on timescales that allow changing subsequent actions.
% AB: weak. \textit{Fast} means that the decision needs to be taken rapidly, in order to respond in real-time with subsequent actions.
\textit{Efficient} means that all information available for decision-making is retrieved and processed in the best possible way.
% AB: \textit{Efficient} means that information relevant to the decision is retrieved and processed in the best possible way.
\vskip2pt
%enrolling them
%in interdisciplinary and intersector doctoral programs. 

%Blurb from doc NCP
% ?The overarching objective of this ITN is to provide high-level training in X to a new generation of high achieving early stage researchers to provide them with the transferable skills necessary for thriving careers in a burgeoning area that underpins innovative technological development across a range of diverse disciplines. This goal will be achieved by a unique combination of ?hands-on? research training, non-academic placements and courses and workshops on scientific and complementary so-called ?soft? skills facilitated by the academic-non-academic composition of the consortium?
 
Examples abound, in research environments in High Energy Physics (HEP) and industry. 
The Large Hadron Collider (LHC) at CERN collides protons up to 30 million times per second: the majority of these events need to be rejected to comply with data processing and storage constraints. 
With the advent of mobile apps for e.g. traffic prediction and fleet control, as well as IoT sensors, the amount of information grows while the resources and time to take a decision using that information do not scale accordingly -- industry faces a similar challenge as HEP. 
\vskip2pt
%%solution
With \acronym, we intend to bring forward a paradigm shift in the way these decisions are made. 

An example of a real-life, real-time decision can be found in traffic predictions: the information on the position of the vehicle and the planned route are transmitted to a central analysis system, the traffic conditions around it are analyzed and a forecast is made. 
All of this needs to be done in the course of less than a second so that the driver can change their route if needed. 

\vskip2pt
\acronym pools the expertise of the leaders of the RTA programs in all four major HEP experiments at the LHC. 
Their knowledge and experience is complemented by a set of industrial partners that apply RTA to automotive traffic, and to applications optimizing IoT sensors for industrial processes, medical applications, computing and instrumentation. 
\acronym will implement a training program for the ESRs will also prepare them as professionals in the fast-evolving areas of DS and RTA.
\acronym will target concrete commercial deliverables such as 
%KKT - ITA
mobile apps using ML for efficient vehicle fleet control, 
%Ximantis - SWE
optimized algorithms for traffic predictions,
%CATHi - DE
and a variety of software for sensors that will improve medical simulation,
%WildTree - SWI
optimize computing resources,
%%Lightbox - I
monitor industrial production
%HeidelbergInstruments - DE
and assemble particles detectors. 
It will benefit the HEP community by providing cutting edge computing technologies and algorithms necessary for the detection and measurement of fundamental particles, and for the discovery of new phenomena that explain e.g. the mystery of the missing matter in the universe. 
%that develop more efficient ways to take decisions on short timescales
